\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/architecture.tex
added target fn requirements to speculative limitations

>>>>

\subsubsection{Target Function Requirements}
The benefits of \speculake rely on the computation performed in the
speculative function being well hidden. To this end we have verified 
certain requirements about the locations that a target function can 
be placed.

First and foremost the target function must be in the instruction cache. 
This does not require that the function is ever run, only loaded. We have 
found that this is not a large barrier to overcome as Intel 
processors aggressively prefetch cache pages~\cite{measuring-cache}
and simple access patterns could be established to ensure
that the required block(s) are accessible.

We have also confirmed that all speculative target code in the payload  
must be stored in executable pages, and that it cannot be stord in non-executable 
data sections.  We suspect that this is again due to caching. The processor
has no reason to cache instructions stored in the data section in the 
instruction cache. If a trigger trains the branch predictor 
to jump to an address in the payload's data section, the payload will not 
be able to fetch the instructions into the execution pipeline.
